---
title: "R Notebook"
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
library(tidyverse)                      # Activate the data science package
library(lubridate)                      # Activate the date management package
load("data/factorml.RData")                   # Load the data
data_ml <- data_ml %>%
    filter(date > "1999-12-31",         # Keep the date with sufficient data points
           date < "2019-01-01") %>%
    arrange(stock_id, date)             # Order the data
data_ml[1:6, 1:6]
```

Type any R code in the chunk, for example:
```{r}
library(reticulate)

np <- import("numpy")
load("data/factorml.RData")
np$save("factorml.npy", data_ml)
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
